What is disputed on the web?

### 2010-02-02 papers/wicow_claimfinder/claimfinder.tex
Fold in Barbara's suggested changes and make minor tweaks of my own

We present a method for the automatic acquisition of a corpus of disputed claims from the web. We consider a claim to be disputed if a page on the web suggests that this claim is wrong and that other people on the web are suggesting that it is true.

@@

\keywords{Sensemaking, Annotation, Argumentation, Web, CSCW}

@@

We identify disputed claims by searching for lexical patterns such as ``the misconception that'' (Section~\ref{findingclaims}). For example, if a page contains the text ``the misconception that {\it the moon is made of cheese}'', this suggests that the author believes that others are saying that the moon is made of cheese, and that the author themselves disputes this claim. In Figure~\ref{templates} we list some of the patterns we used. In practice, many of the strings that match such a pattern are not well-formed disputed claims. We use a statistical classifier to select only those strings that appear to make a well-formed claim.

@@

\begin{figure}[tb]
\begin{center}
  \begin{tabular}{|llll|}
    \hline
    {\bf Frequency$^*$} & {\bf Pattern} & {\bf Pattern} & {\bf Classifier}\\ 
    {\bf on the web} &                   & {\bf Precision} & {\bf Accuracy}\\
    \hline
        \multicolumn{2}{|l}{\it Plausible to not believe it} & &\\
	    & & &\\
        495,000,000 & believe that & 48\%& 65\%\\
        101,000,000 & claim that & 46\%& 72\%\\
       \hline
       \multicolumn{2}{|l}{\it It is notable that others believe it} & &\\
           & & &\\

        40,100,000 & claiming that & 39\% &\\
        30,600,000 & the belief that & &\\
        28,600,000 & believing that & &\\
        11,700,000 & who believe that &&\\
        8,400,000 & who think that &&\\
        \hline
        \multicolumn{2}{|l}{\it Something false} & &\\
	    & & &\\

@@

  \label{templates}
  \caption{Some of the patterns we use to find disputed claims}
\end{figure}

We implemented a three-stage process to build our corpus of disputed claims, each described in the following Sections. We first create a set of lexical patterns such as ``the misconception that'' and ``it is not the case that'' (Section~\ref{patterns}). We then search the Web for these patterns (Section~\ref{searchpattern}) to collect sentences that contain the pattern, followed by some other string. Finally, we filter the resulting strings to give only those that resemble unambiguous falsifiable claims (Section~\ref{filterclaim}).

\begin{figure*}[tb]
\begin{center}
\begin{tabular}{|l|l|l|l|}
  \hline
  & {\bf extracted text} & {\bf valid} & {\bf details} \\
  \hline
  1. & the false claim that {\it won't go away} & no & ``wont go away'' is not a statement \\
  2. & falsely claimed that {\it he didn't do it} & no & ``he'' and ``it'' are unbound referents \\
  3. & falsely claimed that {\it federal labor laws do not apply} & no & object of the verb is not present\\
  4. & false claim that {\it Elvis is alive} despite all evidence & yes & but drop everything after ``despite''\\
  5. & wrongly believe that {\it the moon is made of cheese} & yes & it is a statement about the world \\
\hline
\end{tabular}
\end{center}
\label{filtered}
\caption{We filter out text that does not look like a statement}

@@

We hand-crafted a set of 54 patterns that we hypothesize may indicate that a claim $S$ is disputed, such as ``false claim that $S$'' or or ``it is not true that $S$''. Figure~\ref{templates} shows some of the patterns we use.

This is an instance of pattern matching, a method that has been used extensively for many NLP tasks. Hearst~\cite{Hearst1992} searched for patterns such as ``$X$ such as $Y$'' to infer hyponyms, and Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events; Caraballo~\cite{Caraballo2001} searched for patterns like ``$X$ and $Y$'' to find nouns of the same type, Girju et al~\cite{Girju2003} searched for patterns like ``$X$'s $Y$'' and ``$X$ of the $Y$'' to infer  metronyms. TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
These types of methods differ on how the patterns are generated and on how the extraction of the relevant information is performed. Most often they automatically construct the patterns and often choose them on the basis of
statistics.

In this work we simply start with an initial set of manually crafted search patterns. We then identified additional patterns by searching for the text of known disputed claims, and observing what text commonly occurred as a prefix of a known disputed claim and manually selected those patterns that made sense to us. This technique is inspired by bootstraping algorithms~\cite{jones99bootstrapping,Girju2003,Snow2005} that start with a small number of seed words that belong to a semantic class of interest; these seed words are used to learn the extraction patterns that then can be used to extract new members of the same semantic class. This process is iterated several times and at each times a score is given to each extraction pattern and to each new lexicon entry and only the most reliable ones are retained. In our case, the semantic entity of interest are the claims. Currently, we {\em manually} choose the patterns and claims to retain, i.e., as oppose to most relevant work, we don't {\em learn} the patterns and we don't use a measure of "reliability."

Figure~\ref{templates} shows a subset of the total of 54 patterns that we used. 
For each pattern, the {\it frequency} is the number of pages that Yahoo estimates contain this pattern. The {\it precision} is an estimate of the proportion of text strings matched by the pattern that are unambiguous disputed claims. We discuss precision further in Section~\ref{filterclaim}.

@@

Not all patterns have exactly the same meaning. We grouped our patterns into three loose groups, based on manual inspection of the pages that use them (Figure~\ref{templates}):

@@

Figure~\ref{templates} shows a subset of the {\bf 54} patterns that we used. 
For each pattern, the {\it frequency} is the number of pages that Yahoo estimates contain this pattern. The {\it precision} is an estimate of the proportion of text strings matched by the pattern that are unambiguous disputed claims. We discuss precision further in Section~\ref{filterclaim}.

@@

\begin{figure}
 \begin{center}
  \begin{tabular}{|llll|}
\hline
accuracy      & {\bf \#}    &  {\bf \%}  & {\bf   cum} \\
      \hline
dead on & 16   &   32\%  &   32\% \\
+/-10 d & 9    &   18\%  &   50\% \\
+/-30 d & 12   &   24\%  &   74\% \\
+/-90 d & 3    &   6\%   &   80\% \\
+/-1 yr & 6    &   12\%  &   92\% \\ 
>1 yr   & 4    &   8\%   &   100\% \\ 
\hline
  \end{tabular}
 \end{center}

 \label{dateaccuracy}
 \caption{Accuracy of simple date detection}
\end{figure}

@@

Knowing the rough date when someone believed or disputed something allows us te produce fuzzy time trends Section~\ref{timetrends}. Moreover, it is important to know when people believed particular things, since things that were true in the past may not be true any more (e.g. Elvis was alive in the past, but isn't not).

@@

The {\it P} column in Figure~\ref{templates} shows the precision for different patterns. 
This is the estimated percentage of the strings that match the pattern that are unambiguous falsifiable claims. We estimated the precision of each pattern by randomly selecting 100 strings that match the pattern and then manually marking strings that we subjectively decided were well formed and unambiguous.

@@

The {\it A} column in Figure~\ref{templates} shows how accurately our classifier was able to determine whether any given string matched by a particular pattern is an unambiguous disputable claim. To provide a baseline for what these figures mean, consider that a random classifier would have 50\% accuracy, a classifier that always said ``yes'' would have accuracy equal to the pattern precision (e.g. 62\% for ``the myth that''), and a classifier that always said ``no'' would have accuracy equal to 100 minus, the pattern precision (e.g. 52\% for ``believe that'').

@@

We save the surrounding text, page title, and URL for each of the disputed claims we see made on the web. At present we do not do anything with this data, but we anticipate that it could be useful for many purposes. For example it may be possible to resolve the meaning of ambiguous words or entities based on the words nearby (with have experimented with an algorithm similar to that used by Wikify~\cite{Mihalcea2007}). It is also useful to what person wrote the page, what organization hosted the page, who they link to, what meme-like phrases they make near to the claim, whether the page is written in an ``expert'' style, etc.

\section{Using Disputed Claims}
\label{using}

A corpus of disputed claims could be useful for a variety of applications, including real-time dispute recognition, background dispute analysis agents, and other research tools. Real-time dispute recognition agents could be used, for instance, to alert users when a trusted source disagrees with others, or to provide the user with feedback on how contentious a topic is.

Dispute Finder~\cite{Ennals2010} is one such agent that we are developing to provide real-time dispute recognition to users by identifying disputed claims that appear in web pages. Future iterations of Dispute Finder and other such agents will be designed to work with other media such as television or radio, as well as augmented reality applications. We envision a device that provides real-time feedback to users regarding claims made in a conversation or presentation. Such a device would augment individuals' intuitive recognition of that a disputed claim is being made.

@@

\section{Analyzing the Data}
\label{analysis}
\input{analysis.tex}

We downloaded all text strings that matched each of our 54 patterns for all dates from October 1st 2009 to January 19th 2010, and for January 10th of every year from 2000 to 2010. This gave us a total of 1.8 million text strings, of which 1.1 million were identified by our classifier as being unambiguous disputable claims. Of those 1.1 million text strings, most are repeating claims made elsewhere in the data set.

@@

Figure~\ref{multiplot_nouns} shows the frequency with which particular nouns were discussed in particular years. We obtained these figures by using a part-of-speech tagger to identify nouns in claims found on January 10th of every year from 2000 to 2010. Although the date we searched for was in January, the claims we found are often from other points in the year, due to the fuzzy nature of our date search mechanism (Figure~\ref{dateaccuracy}). We excluded uninteresting nouns such as ``someone'', ``anybody'' and ``something'', and plotted graphs for the ten most disputed nouns. All graphs are plotted on the same scale. The y axis is the number of claims that contained the noun, and the x axis is the year in which the claim was made. It is likely that a Named Entity Recognition algorithm~\cite{Nadeau2007} would produce better results, but even the nouns prove to be quite interesting.

@@

\begin{itemize}
 \item {\bf Obama:} Barack Obama is not a topic of dispute until 2004 when he spoke at the Democratic convention. His level of controversy then peaked in 2008, in the run up to the November 2008 US presidential elections.
 \item {\bf God:} God is always a controversial topic. We theorize that the spike in 2006 may relate to the 2006 publication of the Richard Dawkins book ``the God Delusion''\cite{Dawkins2006} seems to have sparked extra controversy.
 \item {\bf Iraq:} Spikes seem to correspond to the initial invasion in 2003 and the surge in 2007.
 \item {\bf Israel:} The Gaza conflict of 2007 caused a big spike.  
\end{itemize}

@@

   {\bf women} & stay home & 183 \\
               & save vaccine & 85 \\
   \hline
  \end{tabular}
 \end{center}
 \label{cluster-figure}
 \caption{Largest word clusters found for nouns}
\end{figure}

\subsection{Clusters}
\label{clusters}

For each noun, we analyzed the claims about that noun, and produced clusters that represent claims about that noun that seem to be particularly hotly disputed. Rather than clustering claims directly, we instead cluster together words that frequently co-occur. We used an agglomerative clustering algorithm, repeatedly merging the two clusters of words that had the most claims in common.

Figure~\ref{cluster-figure} shows the most frequently occurring word clusters that we found for each noun. Most of these will make sense to people who have been following news in the united states. For example, we see that disputed claims about Obama often talk about his Nobel prize or his birth certificate, and that President Ahmadinejad of Iran did not actually say that Israel should be wiped off the map (which the authors had not previously realized). Some of the word clusters are not particularly interesting - for example many claims talk about the united states, even when that is not an important part of what is disputed.

In the future, we plan to use ideas from textual entailment~\cite{Giampiccolo2007} to cluster claims together directly, and then automatically train a classifier that we can use to identify other claims on the web that are likely to have a similar meaning.

@@

Our research has shown that the web can be used as a corpus to determine what claims people identify as being disputed. Although it is likely that any specific claim found on the web is not authoritative, the web as a whole aggregates the array of views to be found online. Furthermore, because individuals express opinions freely online, a snapshot of the disputed claims online can provide valuable insights into the cultural zeitgeist of the time.

Challenges of creating a comprehensive corpus of disputed claims are many, from data quality to deeper natural language processing challenges such as recognizing textual entailment. We address these in part by taking a high-level statistical view of the data.

The possible applications of a corpus of disputed claims are many and varied. These include real-time dispute recognition, autonomous research agents that operate in the background, and sociocultural research.

Using the claim prefix search technique and text processing, we are able to identify

Our data set currently includes approximately 1.2 million records. We intend to expand this by several orders of magnitude, an improvement that will address issues of data sparsity and enable more robust data processing.

>>>>

We present a method for the automatic acquisition of a corpus of disputed claims from the web. We consider a claim to be disputed if a page on the web suggests that this claim is wrong and that other people believe it is true.

@@

\keywords{dispute, web, credibility}

@@

We identify disputed claims by searching for lexical patterns such as ``the misconception that'' (Section~\ref{findingclaims}). For example, if a page contains the text ``the misconception that {\it the moon is made of cheese}'', this suggests that the author believes that others are saying that the moon is made of cheese, and that the author themselves disputes this claim. In Figure~\ref{templates-fig} we list some of the patterns we used. In practice, many of the strings that match such a pattern are not well-formed disputed claims. We use a statistical classifier to select only those strings that appear to make a well-formed claim.

@@

\begin{figure}[tb]
\begin{center}
  \begin{tabular}{|llll|}
    \hline
    {\bf Frequency$^*$} & {\bf Pattern} & {\bf Pattern} & {\bf Classifier}\\ 
    {\bf on the web} &                   & {\bf Precision} & {\bf Accuracy}\\
    \hline
        &&&\\
        \multicolumn{2}{|l}{\it Plausible to not believe it} & &\\
	    & & &\\
        495,000,000 & believe that & 48\%& 65\%\\
        101,000,000 & claim that & 46\%& 72\%\\
       \hline
       &&&\\
       \multicolumn{2}{|l}{\it It is notable that others believe it} & &\\
           & & &\\

        40,100,000 & claiming that & 39\% &\\
        30,600,000 & the belief that & &\\
        28,600,000 & believing that & &\\
        11,700,000 & who believe that &&\\
        8,400,000 & who think that &&\\
        \hline
	&&&\\
        \multicolumn{2}{|l}{\it Something false} & &\\
	    & & &\\

@@

  \caption{Some of the patterns we use to find disputed claims}
  \label{templates-fig}
\end{figure}

We implemented a three-stage process to build our corpus of disputed claims, each described in the following Sections. We first create a set of lexical patterns such as ``the misconception that'' and ``it is not the case that'' (Section~\ref{patterns}). We then search the Web for these patterns (Section~\ref{searchpattern}) to collect sentences that contain the pattern. Finally, we filter the resulting strings to give only those that resemble unambiguous falsifiable claims (Section~\ref{filterclaim}).

\begin{figure*}[tb]
\begin{center}
\begin{tabular}{|l|l|l|l|}
  \hline
  & {\bf extracted text} & {\bf valid} & {\bf details} \\
  \hline
  1. & the false claim that {\it won't go away} & no & ``wont go away'' is not a statement \\
  2. & falsely claimed that {\it he didn't do it} & no & ``he'' and ``it'' are unbound referents \\
  3. & falsely claimed that {\it federal labor laws do not apply} & no & object of the verb is not present\\
  4. & false claim that {\it Elvis is alive} despite all evidence & yes & but drop everything after ``despite''\\
  5. & wrongly believe that {\it the moon is made of cheese} & yes & it is a statement about the world \\
\hline
\end{tabular}
\end{center}
\caption{We filter out text that does not look like a statement}
\label{filtered}

@@

We hand-crafted a set of 54 patterns that we hypothesize may indicate that a claim $S$ is disputed, such as ``false claim that $S$'' or or ``it is not true that $S$''. Figure~\ref{templates-fig} shows some of the patterns we use.

This is an instance of pattern matching, a method that has been used extensively for many NLP tasks. Hearst~\cite{Hearst1992} searched for patterns such as ``$X$ such as $Y$'' to infer hyponyms, and Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events; Caraballo~\cite{Caraballo2001} searched for patterns like ``$X$ and $Y$'' to find nouns of the same type, Girju et al~\cite{Girju2003} searched for patterns like ``$X$'s $Y$'' and ``$X$ of the $Y$'' to infer  metronyms. TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
These types of methods differ on how the patterns are generated and on how the extraction of the relevant information is performed. Most often they construct the patterns automatically and often choose them on the basis of
statistics.

In this work we simply start with an initial set of manually crafted search patterns. We then identified additional patterns by searching for the text of known disputed claims, and observing what text commonly occurred as a prefix of a known disputed claim and manually selected those patterns that made sense to us. This technique is inspired by bootstrapping algorithms~\cite{jones99bootstrapping,Girju2003,Snow2005} that start with a small number of seed words that belong to a semantic class of interest; these seed words are used to learn the extraction patterns that then can be used to extract new members of the same semantic class. This process is iterated several times and at each times a score is given to each extraction pattern and to each new lexicon entry and only the most reliable ones are retained. In our case, the semantic entity of interest are the claims. Currently, we {\em manually} choose the patterns and claims to retain, i.e., as oppose to most relevant work, we don't {\em learn} the patterns and we don't use a measure of "reliability."

Figure~\ref{templates-fig} shows a subset of the total of 54 patterns that we used. 
For each pattern, the {\it frequency} is the number of pages that Yahoo estimates contain this pattern. The {\it precision} is an estimate of the proportion of text strings matched by the pattern that are unambiguous disputed claims. We discuss precision further in Section~\ref{filterclaim}.

@@

Not all patterns have exactly the same meaning. We grouped our patterns into three loose groups, based on manual inspection of the pages that use them (Figure~\ref{templates-fig}):

@@

@@

\begin{figure}
\vspace{0.5cm}
 \begin{center}
  \begin{tabular}{|llll|}
\hline
{\bf accuracy}      & {\bf count}    &  {\bf percent}  & {\bf cummulative} \\
      \hline
dead on & 16   &   32\%  &   32\% \\
within 10 days & 9    &   18\%  &   50\% \\
within 30 days & 12   &   24\%  &   74\% \\
within 90 days & 3    &   6\%   &   80\% \\
within 1 year & 6    &   12\%  &   92\% \\ 
off by more than 1 year   & 4    &   8\%   &   100\% \\ 
\hline
  \end{tabular}
 \end{center}

 \caption{Accuracy of simple date detection}
 \label{dateaccuracy}
\end{figure}

@@

Knowing the rough date when someone believed or disputed something allows us te produce fuzzy time trends (Section~\ref{timetrends}). Moreover, it is important to know when people believed particular things, since things that were true in the past may not be true any more (e.g. Elvis was alive in the past, but isn't not).

@@

The {\it pattern precision} column in Figure~\ref{templates-fig} shows the estimated precision for different patterns. 
This is the estimated percentage of the strings that match the pattern that are unambiguous falsifiable claims. We estimated the precision of each pattern by randomly selecting 100 strings that match the pattern and then manually marking strings that we subjectively decided were well formed and unambiguous.

@@

The {\it classifier accuracy} column in Figure~\ref{templates-fig} shows how accurately our classifier was able to determine whether any given string matched by a particular pattern is an unambiguous disputable claim. To provide a baseline for what these figures mean, consider that a random classifier would have 50\% accuracy, a classifier that always said ``yes'' would have accuracy equal to the pattern precision (e.g. 62\% for ``the myth that''), and a classifier that always said ``no'' would have accuracy equal to 100 minus, the pattern precision (e.g. 52\% for ``believe that'').

@@

We save the surrounding text, page title, and URL for each of the disputed claims we see made on the web. At present we do not do anything with this data, but we anticipate that it could be useful for many purposes; for example it may be possible to resolve the meaning of ambiguous words or entities based on the words nearby like Wikify~\cite{Mihalcea2007} does. Since many web sites have content written by multiple writers with different degrees of credibility, it is also useful to be able to know which writer disputed a particular claim. Other useful contextual information includes what organization hosted the page, who they link to, what meme-like phrases they make near to the claim, and whether the page is written in an ``expert'' style.

\vspace{0.25cm}
\section{Using Disputed Claims}
\label{using}

A corpus of disputed claims could be useful for many purposes, including real-time dispute recognition, background dispute analysis agents, and other research tools. Real-time dispute recognition agents could be used, for instance, to alert users when a trusted source disagrees with others, or to provide the user with feedback on how contentious a topic is.

Dispute Finder~\cite{Ennals2010} is one such agent that we are developing to provide real-time dispute recognition to users by identifying disputed claims that users encounter in their lives. The current implementation of Dispute Finder is a web browser extension that highlights text on web pages that appears to make a known disputed claim. In future research, we plan to extend Dispute Finder to be able to detect disputed information in television, and in speech that a user hears during conversations. We envision a device that provides real-time feedback to users regarding claims made in a conversation or presentation. Such a device would augment individuals' intuitive recognition of that a disputed claim is being made.

@@

\vspace{0.25cm}
\section{Analyzing the Data}
\label{analysis}
\input{analysis.tex}

We downloaded all text strings that matched each of our 54 patterns for all dates from October 1st 2009 to January 19th 2010, and for January 10th of every year from 2000 to 2010. This gave us a total of 1.8 million text strings, of which 1.1 million were identified by our classifier as being unambiguous disputable claims. This does not mean that there are 1.1 million distinct beliefs that are disputed; many of the claims in our corpus are repeating claims made elsewhere in the corpus.

@@

Figure~\ref{multiplot_nouns} shows the frequency with which particular nouns were discussed in particular years. For example the claim ``Obama is a muslim'' contains the nouns ``Obama'' and ``Muslim''. We used the NLTK~\cite{Bird2009} part-of-speech tagger to identify the nouns found in each of our claims. We then analysed the distribution of noun frequencies in claims associated with January 10th of every year from 2000 to 2010. Although the date we searched for was in January, the claims we found are often from other points in the year, due to the fuzzy nature of our date search mechanism (Figure~\ref{dateaccuracy}). We excluded uninteresting nouns such as ``someone'', ``anybody'' and ``something'', and plotted graphs for the ten most disputed nouns (Figure~\ref{multiplot_nouns}). All graphs are plotted on the same scale. The y axis is the number of claims that contained the noun, and the x axis is the year in which the claim was made. It is likely that a Named Entity Recognition algorithm~\cite{Nadeau2007} would produce better results, but even the nouns prove to be quite interesting.

@@

\begin{itemize}
 \item {\bf Obama:} Barack Obama is not a topic of dispute until 2004 when he spoke at the Democratic convention. His level of controversy then peaked in 2008, in the run up to the November 2008 US presidential elections.
 \item {\bf God:} God is always a controversial topic. We theorize that the spike in 2006 may relate to the 2006 publication of the Richard Dawkins book ``the God Delusion''\cite{Dawkins2006}.
 \item {\bf Iraq:} Spikes seem to correspond to the initial invasion in 2003 and the surge in 2007.
 \item {\bf Israel:} The Gaza conflict of 2007 caused a big spike.  
\end{itemize}

@@

   {\bf women} & stay home & 183 \\
               & save vaccine & 85 \\
   \hline
  \end{tabular}
 \end{center}
 \caption{Largest word clusters found for nouns}
  \label{cluster-figure}

\end{figure}

\subsection{What is Disputed about a Noun?}
\label{clusters}

Once we know what nouns are disputed, it is interesting to know what it is about a noun that is disputed. For example, what is it that people are disputing about ``Obama'' or ``Iraq''? To address this question, we took the set of claims that contained each popular noun (e.g. ``Obama'') and looked for sets of words that occurred together much more frequently than would be expected if claims were formed randomly. For example in our claims about ``Obama'', we found the word cluster ``health care'' because most claims about Obama that contain the word ``health'' also contain the word ``care'' and vice-versa.

Figure~\ref{cluster-figure} shows the most frequently occurring word clusters that we found for each noun. For each cluster, the count is the number of claims about that noun that contain all of the words. Most of these will make sense to people who have been following news in the United States. For example, we see that disputed claims about Obama often talk about his Nobel Prize or his birth certificate, and we see that President Ahmadinejad of Iran did not actually say that Israel should be wiped off the map (which the authors had not previously realized). Some of the word clusters are not particularly interesting; for example many claims talk about the united states, even when that is not an important part of what is disputed.

In the future, we plan to use ideas from textual entailment~\cite{Giampiccolo2007} to cluster claims together directly, and then automatically train a classifier that we can use to identify other claims on the web that are likely to have a similar meaning. This will allow us to better attack some of the problems we outlined in Section~\ref{using}.

@@

Our research has shown that the web can be used as a corpus to determine what claims people identify as being disputed. Although it is likely that any specific claim found on the web is not authoritative, the web as a whole aggregates the collection of views that can be be found online. Furthermore, because individuals express opinions freely online, a snapshot of the disputed claims online can provide valuable insights into the cultural zeitgeist of the time.

Creating a comprehensive corpus of disputed claims presents many challenges: how to create patterns, how to search for patterns, how to avoid malformed sentences, how to resolve or filter out ambiguous claims, how to determine if two claims are paraphrases, and how to determine if text on the web contains a claim that our database says is disputed. For each of these tasks, we have implemented enough to get useful results, but there is much scope to do things better.

There are many possible applications for a corpus of disputed claims. These include real-time dispute recognition, autonomous research agents that operate in the background, and sociocultural research.

Our data set currently includes approximately 1.1 million records. We intend to expand this by several orders of magnitude.
